---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ftDK

The goal of `ftDK` is to provide an easy wrapper in R for the API of the Danish Parliament. You can see the website for the API her: http://www.ft.dk/AabneData.aspx

## Installation

You can install ftDK from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mikkelkrogsholm/ftDK")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ftDK)

# See the avaible endpoints 
see_endpoints()

# Lets fetch the data for the "afstemning" endpoint
ft_data  <- get_ft("afstemning")

# Lets have a look at the data
ft_data

```

This is a first version of the package. It does the job of pulling data from the API.
Next up will be to create more elaborate functions. Please contribute to the package if you can.
